---
title: "Dota 2 Stats 1.5"
output: html_document
date: "2023-12-23"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r packages used}
library(tidyverse)
library(readxl)
```


## HEROES

```{r Heroes, echo = TRUE}

Abaddon <- "Abbadon"
Alchemist <- "Alchemist"
Ancient_Apparition <- "Ancient_Apparition"
Anti_Mage <- "Anti_Mage"
Arc_Wardern <- "Arc_Warden"
Axe <- "Axe"
Bane <- "Bane"
Batrider <- "Batrider"
Beastmaster <- "Beastmaster"
Bloodseeker <- "Bloodseeker"
Bounty_Hunter <- "Bounty_Hunter"
Brewmaster <- "Brewmaster"
Bristleback <- "Bristleback"
Broodmother <- "Broodmother"
Centaur_Warrunner <- "Centaur_Warruner"
Chaos_Knight <- "Chaos_Knight"
Chen <- "Chen"
Clinkz <- "Clinkz"
Clockwerk <- "Clockwerk"
Crystal_Maiden <- "Crystal_Maiden"
Dark_Seer <- "Dark_Seer"
Dark_Willow <- "Dark_Willow"
Dawnbreaker <- "Dawnbreaker"
Dazzle <- "Dazzle"
Death_Prophet <- "Death_Prophet"
Disruptor <- "Disruptor"
Doom <- "Doom"
Dragon_Knight <- "Dragon_Knight"
Drow_Ranger <- "Drow_Ranger"
Earth_Spirit <- "Earth_Spirit"
Earthshaker <- "Earthshaker"
Elder_Titan <- "Elder_Titan"
Ember_Spirit <- "Ember_Spirit"
Enchantress <- "Enchantress"
Enigma <- "Enigma"
Faceless_Void <- "Faceless_Void"
Grimstroke <- "Grimstroke"
Gyrocopter <- "Gyrocopter"
Hoodwink <- "Hoodwink"
Huskar <- "Huskar"
Invoker <- "Invoker"
IO <- "IO"
Jakiro <- "Jakiro"
Juggernaut <- "Juggernaut"
Keeper_of_the_Light <- "Keeper_of_the_Light"
Kunkka <- "Kunkka"
Legion_Commander <- "Legion_Commander"
Leshrac <- "Leshrac"
Lich <- "Lich"
Lifestealer <- "Lifestealer"
Lina <- "Lina"
Lion <- "Lion"
Lone_Druid <- "Lone_Druid"
Luna <- "Luna"
Lycan <- "Lycan"
Magnus <- "Magnus"
Marci <- "Marci"
Mars <- "Mars"
Medusa <- "Medusa"
Meepo <- "Meepo"
Mirana <- "Mirana"
Monkey_King <- "Monkey_King"
Morphling <- "Morphling"
Muerta <- "Muerta"
Naga_Siren <- "Naga_Siren"
Natures_Prophet <- "Natures_Prophet"
Necrophos <- "Necrophos"
Night_Stalker <- "Night_Stalker"
Nyx_Assassin <- "Nyx_Assassin"
Ogre_Magi <- "Ogre_Magi"
Omniknight <- "Omniknight"
Oracle <- "Oracle"
Outworld_Destroyer <- "Outworld_Destroyer"
Pangolier <- "Pangolier"
Phantom_Assassin <- "Phanton_Assassin"
Phantom_Lancer <- "Phantom_Lancer"
Phoenix <- "Phoenix"
Primal_Beast <- "Primal_Beast"
Puck <- "Puck"
Pudge <- "Pudge"
Pugna <- "Pugna"
Queen_of_Pain <- "Queen_of_Pain"
Razor <- "Razor"
Riki <- "Riki"
Rubick <- "Rubick"
Sand_King <- "Sand_King"
Shadow_Demon <- "Shadow_Demon"
Shadow_Fiend <- "Shadow_Fiend"
Shadow_Shaman <- "Shadow_Shaman"
Silencer <- "Silencer"
SKywrath_Mage <- "Skywrath_Mage"
Slardar <- "Slardar"
Slark <- "Slark"
Snapfire <- "Snapfire"
Sniper <- "Sniper"
Spectre <- "Spectre"
Spirit_Breaker <- "Spirit_Breaker"
Storm_Spirit <- "Storm_Spirit"
Sven <- "Sven"
Techies <- "Techies"
Templar_Assassin <- "Templar_Assassin"
Terrorblade <- "Terrorblade"
Tidehunter <- "Tidehunter"
TimbersaW <- "Timbersaw"
Tinker <- "Tinker"
Tiny <- "Tiny"
Treant_Protector <- "Treant_Protector"
Troll_Warlord <- "Troll_Warlord"
Tusk <- "Tusk"
Underlord <- "Underlord"
Undying <- "Undying"
Ursa <- "Ursa"
Vengeful_Spirit <- "Vengeful_Spirit"
Venomancer <- "Venomancer"
Viper <- "Viper"
Visage <- "Visage"
Void_Spirt <- "Void_Spirit"
Warlock <- "Warlock"
Weaver <- "Weaver"
Windranger <- "Windranger"
Winter_Wyvern <- "Winter_Wyvern"
Witch_Doctor <- "Witch_Doctor"
Wraith_King <- "Wraith_King"
Zeus <- "Zeus"
```



## Games Data Frame

```{r}
Radiant_Safe_Lane <- c(Phantom_Lancer, Juggernaut, Weaver, Lycan, Phantom_Lancer, Faceless_Void, Phantom_Lancer, Luna, Naga_Siren, Bloodseeker, Phantom_Assassin, Juggernaut, Anti_Mage, Troll_Warlord, Riki, Bloodseeker, Lifestealer, Juggernaut, Slark, Phantom_Assassin, Juggernaut, Abaddon, Drow_Ranger, Drow_Ranger, Sniper, Juggernaut, Brewmaster, Sniper, Faceless_Void, Sven, Ember_Spirit, Terrorblade, Spectre, Sniper, Faceless_Void, Muerta, Juggernaut, Hoodwink, Sven, Outworld_Destroyer, Phantom_Assassin, Sniper, Slark, Natures_Prophet, Monkey_King, Drow_Ranger, Lifestealer, Lifestealer, Faceless_Void, Phantom_Lancer, Viper, Slark, Anti_Mage, Phantom_Assassin, Lifestealer, Drow_Ranger, Clinkz, Anti_Mage, Juggernaut, Sven, Monkey_King, Muerta, Juggernaut, Anti_Mage, Lifestealer, Wraith_King, Juggernaut, Chaos_Knight, Ursa, Wraith_King)

length(Radiant_Safe_Lane)
```

```{r}
Radiant_Mid_Lane <- c(Sniper, Sniper, Windranger, Queen_of_Pain, Shadow_Fiend, Sniper, Arc_Wardern, Earthshaker, Disruptor, Zeus, Lina, Mars, Centaur_Warrunner, Pudge, Omniknight, Huskar, Sniper, Puck, Templar_Assassin, Keeper_of_the_Light, Huskar, Invoker, Leshrac, Earthshaker, Hoodwink, Necrophos, Windranger, Shadow_Fiend, Natures_Prophet, Necrophos, Pudge, Bounty_Hunter, Puck, Outworld_Destroyer, Shadow_Fiend, Puck, Bounty_Hunter, Lina, Invoker, Medusa, Windranger, Puck, Viper, Ursa, Windranger, Natures_Prophet, Legion_Commander, Pangolier, Lone_Druid, Natures_Prophet, Bounty_Hunter, Shadow_Fiend, Storm_Spirit, Phoenix, Shadow_Shaman, Legion_Commander, Rubick, Sniper, Sniper, Pudge, Zeus, Void_Spirt, Dark_Willow, Outworld_Destroyer, Void_Spirt, TimbersaW, Viper, Shadow_Fiend, Silencer, Necrophos)

length(Radiant_Mid_Lane)
```

```{r}
Radiant_Off_Lane <- c(Chaos_Knight, Legion_Commander, Centaur_Warrunner, Night_Stalker, Legion_Commander, Centaur_Warrunner, Elder_Titan, Axe, Invoker, Abaddon, Lycan, Undying, Axe, Undying, Abaddon, Abaddon, Ogre_Magi, Slardar, Razor, Legion_Commander, Earthshaker, Legion_Commander, Slardar, Dragon_Knight, TimbersaW, Sand_King, Kunkka, Abaddon, Dragon_Knight, Death_Prophet, Tidehunter, Death_Prophet, Death_Prophet, Mars, Nyx_Assassin, TimbersaW, Mars, Pudge, Slardar, Slardar, Dragon_Knight, Brewmaster, Razor, Morphling, Abaddon, Razor, Razor, Beastmaster, Abaddon, Dragon_Knight, Night_Stalker, Spirit_Breaker, Centaur_Warrunner, Legion_Commander, Slardar, Pudge, Tidehunter, Legion_Commander, Slardar, Axe, Dragon_Knight, Axe, Legion_Commander, Brewmaster, Dragon_Knight, Viper, Necrophos, Axe, Kunkka, Bounty_Hunter)

length(Radiant_Off_Lane)
```

```{r}
Radiant_Support <- c(Treant_Protector, Silencer, Dazzle, Lion, Magnus, Ogre_Magi, Winter_Wyvern, Crystal_Maiden, Jakiro, Ogre_Magi, Witch_Doctor, Omniknight, Witch_Doctor, Vengeful_Spirit, SKywrath_Mage, Jakiro, Shadow_Shaman, Abaddon, Witch_Doctor, Silencer, Witch_Doctor, Pudge, Mirana, Venomancer, Jakiro, Jakiro, Bounty_Hunter,Witch_Doctor, Dazzle, Ancient_Apparition, Enigma, Ogre_Magi, Dazzle, Earthshaker, Witch_Doctor, Jakiro, Rubick, Natures_Prophet, Natures_Prophet, Jakiro, Ancient_Apparition, Sand_King, Spirit_Breaker, Dragon_Knight, Lion, Shadow_Shaman, Spirit_Breaker, Ancient_Apparition, Ogre_Magi, Jakiro, Earthshaker, Witch_Doctor, SKywrath_Mage, Shadow_Shaman, Venomancer,Pugna, Natures_Prophet, Tusk, Tusk, Dark_Willow, Grimstroke, Witch_Doctor, Vengeful_Spirit, Ogre_Magi, Rubick, Abaddon, Snapfire, Oracle, Dazzle, Ancient_Apparition)

length(Radiant_Support)
```

```{r}
Radiant_Hard_Support <- c(Disruptor, SKywrath_Mage, Witch_Doctor, Jakiro, Witch_Doctor, Windranger, Ancient_Apparition, SKywrath_Mage, Winter_Wyvern, Jakiro, Ancient_Apparition, Ogre_Magi, Disruptor, Witch_Doctor, Witch_Doctor, Lich, Witch_Doctor, Ancient_Apparition, Shadow_Demon, Spirit_Breaker, Dawnbreaker, Lich, Ancient_Apparition, Ancient_Apparition, Warlock, Lion, Ancient_Apparition, Ancient_Apparition, Pudge, Sand_King, Dazzle, Dazzle, Pudge, Rubick, Earth_Spirit, Shadow_Shaman, Lion, Treant_Protector, Pudge, Pudge, Jakiro, Jakiro, Pugna, Warlock, Jakiro, Dazzle, Crystal_Maiden, Jakiro, Shadow_Shaman, Keeper_of_the_Light, Shadow_Shaman, Disruptor, Natures_Prophet, Lion, Jakiro, Crystal_Maiden, Vengeful_Spirit, Witch_Doctor, Venomancer, Jakiro, Ogre_Magi, Vengeful_Spirit, Ancient_Apparition, Lion, Silencer, Jakiro, Ancient_Apparition, Venomancer, Shadow_Shaman, Shadow_Shaman)

length(Radiant_Hard_Support)
```






```{r}

Dire_Safe_Lane <- c(Faceless_Void, Natures_Prophet, Faceless_Void, Chaos_Knight, Juggernaut, Juggernaut, Ursa, Juggernaut, Phantom_Lancer, Faceless_Void, Riki, Faceless_Void, Sniper, Weaver, Lifestealer, Faceless_Void, Spectre, Weaver, Drow_Ranger, Monkey_King, Luna, Monkey_King, Juggernaut, Phantom_Assassin, Phantom_Lancer, Drow_Ranger, Ogre_Magi, Slardar, Phantom_Assassin, Zeus, Luna, Spectre, Slark, Phantom_Assassin, Spectre, Ursa, Faceless_Void, Lifestealer, Ursa, Weaver, Medusa, Riki, Spectre, Juggernaut, Anti_Mage, Juggernaut, Faceless_Void, Wraith_King, Wraith_King, Phantom_Assassin, Medusa, Anti_Mage, Clinkz, Sniper, Troll_Warlord, Phantom_Assassin, Anti_Mage, Spectre, Wraith_King, Weaver, Ursa, Sniper, Morphling, Phantom_Lancer, Troll_Warlord, Muerta, Anti_Mage, Drow_Ranger, Mirana, Sniper)

length(Dire_Safe_Lane)
```

```{r}

Dire_Mid_Lane <- c(Shadow_Fiend, Spirit_Breaker, Luna, Invoker, Lone_Druid, Vengeful_Spirit, Warlock, Necrophos, Outworld_Destroyer, Weaver, Dazzle, Drow_Ranger, Necrophos, Silencer, Sniper, Necrophos, Puck, Keeper_of_the_Light, Zeus, Dawnbreaker, Viper, Drow_Ranger, Invoker, Necrophos, Weaver, Naga_Siren, Outworld_Destroyer, Bristleback, Clinkz, Viper, Legion_Commander, Lion, Windranger, Puck, Spirit_Breaker, Windranger, Puck, Puck, Sniper, Chaos_Knight, Ogre_Magi, Arc_Wardern, Void_Spirt, Primal_Beast, Sniper, Death_Prophet, Necrophos, Shadow_Fiend, Outworld_Destroyer, Invoker, Silencer, Doom, Dragon_Knight, Muerta, Lina, Bounty_Hunter, Sniper, Lina, Arc_Wardern, Elder_Titan, Queen_of_Pain, Pugna, Lion, Sniper, Sniper, Riki, Silencer, Spectre, Storm_Spirit, Pudge)

length(Dire_Mid_Lane)
```

```{r}

Dire_Off_Lane <- c(Slardar, Dragon_Knight, Earthshaker, Dragon_Knight, Abaddon, Dragon_Knight, Tidehunter, Ogre_Magi, Chaos_Knight, Ursa, Beastmaster, Pudge, Slardar, Sand_King, Wraith_King, Tusk, Legion_Commander, Magnus, TimbersaW, Abaddon, Centaur_Warrunner, Undying, Axe, Mars, Slardar, Slardar, Queen_of_Pain, Pudge, Sand_King, Pudge, Bristleback, Underlord, Magnus, Death_Prophet, Death_Prophet, Doom, TimbersaW, Treant_Protector, Treant_Protector, Windranger, Pudge, Legion_Commander, Tusk, Centaur_Warrunner, Dragon_Knight, Underlord, Tidehunter, Primal_Beast, Slardar, Tusk, Bristleback, Gyrocopter, Night_Stalker, Axe, Wraith_King, Kunkka, Underlord, Clockwerk, Centaur_Warrunner, Wraith_King, Sand_King, Primal_Beast, Razor, Abaddon, Pudge, Spirit_Breaker, Doom, Abaddon, Zeus, Kunkka)

length(Dire_Off_Lane)
```

```{r}
Dire_Support <- c(Spirit_Breaker, Ancient_Apparition, Invoker, Earthshaker, Shadow_Shaman, Invoker, Omniknight, Grimstroke, Dark_Willow, Pudge, Treant_Protector, Silencer, Silencer, Jakiro, Shadow_Shaman, Spirit_Breaker, Treant_Protector, Gyrocopter, Vengeful_Spirit, Lich, Dazzle, Venomancer, Hoodwink, Shadow_Shaman, Earthshaker, Tusk, Witch_Doctor, Grimstroke, Earthshaker, Lich, Lion, Zeus, Witch_Doctor, Ogre_Magi, Ogre_Magi, Lion, Ancient_Apparition, Lich, Enigma, Lion, Undying, Treant_Protector, Jakiro, Ancient_Apparition, Witch_Doctor, Jakiro, Jakiro, Pudge, Crystal_Maiden, Ogre_Magi, Techies, Natures_Prophet, Ancient_Apparition, Ancient_Apparition, Crystal_Maiden, Mirana, Witch_Doctor, Ancient_Apparition, Lich, Nyx_Assassin, Spirit_Breaker, Ancient_Apparition, Bounty_Hunter, Ancient_Apparition, Shadow_Shaman, Grimstroke, Undying, Ancient_Apparition, Ogre_Magi, Lion)

length(Dire_Support)
```

```{r}
Dire_Hard_Support <- c(Jakiro, Zeus, Ancient_Apparition, Lich, Disruptor, Jakiro, Jakiro, Ancient_Apparition, Ogre_Magi, Crystal_Maiden, Jakiro, Hoodwink, Ancient_Apparition, Treant_Protector, Dazzle, Witch_Doctor, Ancient_Apparition, Tusk, Ancient_Apparition, Grimstroke, Warlock, Ancient_Apparition, Shadow_Shaman, Disruptor, Grimstroke, Witch_Doctor, Lion, Silencer, Ancient_Apparition, Spirit_Breaker, Ancient_Apparition, Pugna, Lich, Magnus, Lion, Phantom_Assassin, Warlock, Ancient_Apparition, Ancient_Apparition, Shadow_Shaman, Earthshaker, Shadow_Shaman, Witch_Doctor, Witch_Doctor, Shadow_Shaman, Grimstroke, Venomancer, Shadow_Shaman, Hoodwink, Crystal_Maiden, Ancient_Apparition, Ancient_Apparition, Techies, SKywrath_Mage, Pugna, Ancient_Apparition, Pudge, Phoenix, Shadow_Demon, Ancient_Apparition, Lion, Dazzle, Phoenix, Crystal_Maiden, Bristleback, Crystal_Maiden, Warlock, Spirit_Breaker, Ancient_Apparition, Dazzle)

length(Dire_Hard_Support)
```

```{r}

Game_Time <- hms(c("00:29:05", "00:52:12", "00:46:27", "00:44:11", "00:45:01", "00:43:51", "00:49:17", "00:45:52", "00:28:08", "00:43:30", "00:39:42", "00:54:48", "00:53:08", "00:34:28", "00:25:05", "00:34:06", "01:15:50", "00:43:15", "00:57:24", "00:33:05", "00:56:03", "00:48:00", "00:53:24", "01:04:46", "00:42:53", "00:43:08", "00:38:13", "00:38:19", "00:47:52", "00:59:20", "00:40:47", "00:39:01", "00:52:32", "00:37:10", "00:45:37", "00:35:16", "00:47:44", "00:46:30", "00:59:24", "00:44:51", "00:42:48", "00:42:08", "00:23:12", "00:34:19", "00:32:24", "00:31:36", "00:32:52", "00:28:48", "00:42:46", "00:43:13", "00:52:32", "00:33:50", "01:03:20", "00:53:00", "00:43:16", "00:34:40", "00:45:06", "00:41:38", "00:35:43", "00:30:08", "01:03:02", "00:47:55", "00:40:37", "00:40:38", "00:31:52", "00:26:07", "00:31:26", "00:43:27", "00:58:16", "00:52:57"))


Radiant_Win_TF <- c(FALSE, FALSE, TRUE, FALSE, TRUE, TRUE, TRUE, FALSE, TRUE, TRUE, TRUE, TRUE, FALSE, TRUE, TRUE, TRUE, TRUE, TRUE, FALSE, TRUE, FALSE, TRUE, TRUE, TRUE, FALSE, TRUE, FALSE, TRUE, TRUE, TRUE, FALSE, TRUE, FALSE, FALSE, TRUE, TRUE, FALSE, FALSE, TRUE, FALSE, FALSE, TRUE, TRUE, FALSE, TRUE, TRUE, TRUE, TRUE, FALSE, FALSE, FALSE, FALSE, TRUE, TRUE, TRUE, TRUE, FALSE, TRUE, TRUE, TRUE, TRUE, TRUE, TRUE, FALSE, TRUE, TRUE, TRUE, FALSE, TRUE, FALSE)



Match_ID <- c(7520462907, 7520488996, 7522003567, 7522030423, 7522055031, 7523745337, 7523790773, 7523842305, 7523879924, 7523952083, 7524883502, 7524965364, 7525034182, 7525116921, 7525184949, 7528824929, 7528850710, 7528911024, 7530202683, 7530255597, 7530293064, 7530317966, 7531696715, 7531772220, 7531809136, 7533224731)


Dota_2_Stats_ALT <- data.frame(Radiant_Safe_Lane, Radiant_Mid_Lane, Radiant_Off_Lane, Radiant_Support, Radiant_Hard_Support, Dire_Safe_Lane, Dire_Mid_Lane, Dire_Off_Lane, Dire_Support, Dire_Hard_Support, Radiant_Win_TF) 


glimpse(Dota_2_Stats_ALT)
```



## Unlisted Hero Counts


```{r Unlisted Hero Counts, echo = TRUE}
Unlisted_Dota_2_Data <- table(unlist(Dota_2_Stats_ALT))


Sorted_Unlisted_Table <- Unlisted_Dota_2_Data[order(Unlisted_Dota_2_Data, decreasing = TRUE)]


print(Sorted_Unlisted_Table)

```


##
```{r}



```

## Safe Lane Carry Winners Combined and Counted


```{r}
Radiant_Safe_Lane_Winners <- Dota_2_Stats_ALT %>%
  filter(Radiant_Win_TF == TRUE) %>%
  select(Radiant_Safe_Lane)


Renamed_Radiant_Safe_Lane_Winners <- rename(Radiant_Safe_Lane_Winners, Safe_Lane = "Radiant_Safe_Lane")


Dire_Safe_Lane_Winners <- Dota_2_Stats_ALT %>%
  filter(Radiant_Win_TF == FALSE) %>%
  select(Dire_Safe_Lane)


Renamed_Dire_Safe_Lane_Winners <- rename(Dire_Safe_Lane_Winners, Safe_Lane = "Dire_Safe_Lane")


Safe_Lane_Winners_Combined <- rbind(Renamed_Radiant_Safe_Lane_Winners, Renamed_Dire_Safe_Lane_Winners)


Safe_Lane_Winners_Combined_Counted <- Safe_Lane_Winners_Combined %>%
  count(Safe_Lane, name = "Wins", sort = TRUE)


Safe_Lane_Winners_Combined_Counted
```


## Safe Lane Carry Totals Combined and Counted


```{r}
Radiant_Safe_Lane_Hero_Totals <-Dota_2_Stats_ALT %>%
  select(Radiant_Safe_Lane) 


Renamed_Radiant_Safe_Lane_Hero_Totals <- Radiant_Safe_Lane_Hero_Totals %>%
  rename(Safe_Lane = "Radiant_Safe_Lane")


Dire_Safe_Lane_Hero_Totals <- Dota_2_Stats_ALT %>%
  select(Dire_Safe_Lane) 
  

Renamed_Dire_Safe_Lane_Hero_Totals <- Dire_Safe_Lane_Hero_Totals %>%
  rename(Safe_Lane = "Dire_Safe_Lane")


Safe_Lane_Carry_Totals_Combined <- rbind(Renamed_Radiant_Safe_Lane_Hero_Totals, Renamed_Dire_Safe_Lane_Hero_Totals)


Safe_Lane_Carry_Totals_Combined_Counted <- Safe_Lane_Carry_Totals_Combined %>%
  count(Safe_Lane, name = "Total_Games", sort = TRUE)


Safe_Lane_Carry_Totals_Combined_Counted

```


## Safe Lane Carry Percent Win


```{r}
Safe_Lane_Carry_Wins_And_Totals <- merge(x = Safe_Lane_Winners_Combined_Counted, y = Safe_Lane_Carry_Totals_Combined_Counted, by = "Safe_Lane", all.y = TRUE)


Safe_Lane_Carry_Win_Percentages <- Safe_Lane_Carry_Wins_And_Totals %>%
  mutate(Win_Percentage = Wins / Total_Games)


Safe_Lane_Carry_Win_Percentages_Arranged <- arrange(Safe_Lane_Carry_Win_Percentages,desc(Win_Percentage), desc(Total_Games))


Safe_Lane_Carry_Win_Percentages_Arranged

Safe_Lane_Carry_Win_Percentages_Ranked <- Safe_Lane_Carry_Win_Percentages %>%
  mutate(Ranking = Wins + 5 * Win_Percentage / Total_Games + 5) %>%
  arrange(desc(Ranking))

Safe_Lane_Carry_Win_Percentages_Ranked

Safe_Lane_Carry_Win_Percentages_Ranked_2 <- Safe_Lane_Carry_Win_Percentages %>%
  mutate(Ranking_2 = Wins * Wins / Total_Games) %>%
  arrange(desc(Ranking_2))
Safe_Lane_Carry_Win_Percentages_Ranked_2
```


## Radiant Safe Lane Combos


```{r}

Radiant_Safe_Lane_Winning_Combos <-  Dota_2_Stats_ALT %>%
  filter(Radiant_Win_TF == TRUE) %>%
  select(Radiant_Safe_Lane, Radiant_Hard_Support)

Radiant_Safe_Lane_Winning_Combos

  




Renamed_Radiant_Safe_Lane_Combos <- Radiant_Safe_Lane_Winning_Combos %>%
  rename(
    Hard_Support = Radiant_Hard_Support, Safe_Lane = Radiant_Safe_Lane
  )
print(Renamed_Radiant_Safe_Lane_Combos)
Radiant_Bot_Combos <-Dota_2_Stats_ALT %>%
  select(Radiant_Safe_Lane, Radiant_Hard_Support)
Radiant_Bot_Combos
Renamed_Radiant_Bot_Combos <- rename(Radiant_Bot_Combos, Safe_Lane = Radiant_Safe_Lane, Hard_Support = Radiant_Hard_Support)
Renamed_Radiant_Bot_Combos
```

## Dire


```{r}
Dire_Safe_Lane_Winning_Combos <-  Dota_2_Stats_ALT %>%
  filter(Radiant_Win_TF == FALSE) %>%
  select(Dire_Safe_Lane, Dire_Hard_Support)


Renamed_Dire_Safe_Lane_Combos <- Dire_Safe_Lane_Winning_Combos %>%
  rename(
    Safe_Lane = Dire_Safe_Lane, Hard_Support = Dire_Hard_Support
  )


Dire_Top_Combos <-Dota_2_Stats_ALT %>%
  select(Dire_Safe_Lane, Dire_Hard_Support)
Dire_Top_Combos


Renamed_Dire_Top_Combos <- rename(Dire_Top_Combos, Safe_Lane = Dire_Safe_Lane, Hard_Support = Dire_Hard_Support)


Renamed_Dire_Top_Combos
```


## Safe Lane Combos Combined


```{r}
Safe_Lane_Combos_Combined <- rbind(Renamed_Radiant_Bot_Combos, Renamed_Dire_Top_Combos)


Safe_Lane_Combos_Combined_Counted <- Safe_Lane_Combos_Combined %>%
  count(Safe_Lane, Hard_Support, name = "Total_Games", sort = TRUE)


print(Safe_Lane_Combos_Combined_Counted)
```


## Winning Safe Combos


```{r}
Safe_Lane_Winning_Combos_Combined <- rbind(Renamed_Radiant_Safe_Lane_Combos, Renamed_Dire_Safe_Lane_Combos)

Safe_Lane_Winning_Combos_Combined_Counted <- Safe_Lane_Winning_Combos_Combined %>%
  count(Safe_Lane, Hard_Support, name = "Wins", sort = TRUE) 

print(Safe_Lane_Winning_Combos_Combined_Counted)

```


## Join Tinkering with Safe Winners and Safe Combos


```{r}
Safe_Lane_Combos <- merge(x = Safe_Lane_Winning_Combos_Combined_Counted, y = Safe_Lane_Combos_Combined_Counted, by = c("Safe_Lane","Hard_Support"), all.y = TRUE)


Safe_Lane_Combos
```


## FINALLY MADE WHAT I WANTED: (a version at least) of Safe Lane Combos win percentage


```{r}
Safe_Lane_Combos_Win_Percentages <- Safe_Lane_Combos %>%
  mutate(Win_Percentage = Wins / Total_Games)


Safe_Lane_Combos_Win_Percentages_Arranged <- arrange(Safe_Lane_Combos_Win_Percentages,desc(Win_Percentage), desc(Total_Games))

Safe_Lane_Combos_Win_Percentages_Ranked_2 <- Safe_Lane_Combos_Win_Percentages %>%
  mutate(Ranking_2 = Wins * Wins / Total_Games) %>%
  arrange(desc(Ranking_2))
Safe_Lane_Combos_Win_Percentages_Ranked_2

```





## Off Lane Winning Combos


```{r}
Radiant_Off_Lane_Winning_Combos <- Dota_2_Stats_ALT %>%
  filter(Radiant_Win_TF == TRUE) %>%
  select(Radiant_Off_Lane, Radiant_Support)


Renamed_Radiant_Off_Lane_Winning_Combos <- Radiant_Off_Lane_Winning_Combos %>%
  rename(
    Support = Radiant_Support, Off_Lane = Radiant_Off_Lane
  )


Dire_Off_Lane_Winning_Combos <- Dota_2_Stats_ALT %>%
  filter(Radiant_Win_TF == FALSE) %>%
  select(Dire_Off_Lane, Dire_Support)


Renamed_Dire_Off_Lane_Winning_Combos <- Dire_Off_Lane_Winning_Combos %>%
  rename(
    Support = Dire_Support, Off_Lane = Dire_Off_Lane
  )


Off_Lane_Winning_Combos_Combined <- rbind(Renamed_Radiant_Off_Lane_Winning_Combos, Renamed_Dire_Off_Lane_Winning_Combos)


Off_Lane_Winning_Combos_Combined_Counted <- Off_Lane_Winning_Combos_Combined %>%
  count(Off_Lane, Support, name = "Wins", sort = TRUE)


Dire_Bot_Combos <- Dota_2_Stats_ALT %>%
  select(Dire_Off_Lane, Dire_Support)


Renamed_Dire_Bot_Combos <- rename(Dire_Bot_Combos, Off_Lane = Dire_Off_Lane, Support = Dire_Support)


Radiant_Top_Combos <- Dota_2_Stats_ALT %>%
  select(Radiant_Off_Lane, Radiant_Support)


Renamed_Radiant_Top_Combos <- rename(Radiant_Top_Combos, Off_Lane = Radiant_Off_Lane, Support = Radiant_Support)


Off_Lane_Combos_Combined <- rbind(Renamed_Radiant_Top_Combos, Renamed_Dire_Bot_Combos)
Off_Lane_Combos_Combined
Off_Lane_Combos_Combined_Counted <- Off_Lane_Combos_Combined %>%
  count(Off_Lane, Support, name = "Total_Games", sort = TRUE)


Off_Lane_Combos <- merge(x = Off_Lane_Winning_Combos_Combined_Counted, y = Off_Lane_Combos_Combined_Counted, by = c("Off_Lane","Support"), all.y = TRUE)
Off_Lane_Combos


Off_Lane_Combos_Win_Percentages <- Off_Lane_Combos %>%
  mutate(Win_Percentage = Wins / Total_Games)


Off_Lane_Combos_Win_Percentages_Arranged <- arrange(Off_Lane_Combos_Win_Percentages,desc(Win_Percentage), desc(Total_Games))


Off_Lane_Combos_Win_Percentages_Arranged

Off_Lane_Combos_Win_Percentages_Ranked_2 <- Off_Lane_Combos_Win_Percentages %>%
  mutate(Ranking_2 = Wins * Wins / Total_Games) %>%
  arrange(desc(Ranking_2))
Off_Lane_Combos_Win_Percentages_Ranked_2
```

## Mid Winners


```{r}
Radiant_Mid_Lane_Winners <- Dota_2_Stats_ALT %>%
  filter(Radiant_Win_TF == TRUE) %>%
  select(Radiant_Mid_Lane)


Renamed_Radiant_Mid_Lane_Winners <- rename(Radiant_Mid_Lane_Winners, Mid_Lane = "Radiant_Mid_Lane")


Dire_Mid_Lane_Winners <- Dota_2_Stats_ALT %>%
  filter(Radiant_Win_TF == FALSE) %>%
  select(Dire_Mid_Lane)


Renamed_Dire_Mid_Lane_Winners <- rename(Dire_Mid_Lane_Winners, Mid_Lane = "Dire_Mid_Lane")


Mid_Lane_Winners_Combined <- rbind(Renamed_Radiant_Mid_Lane_Winners, Renamed_Dire_Mid_Lane_Winners)
Mid_Lane_Winners_Combined_Counted <- Mid_Lane_Winners_Combined %>%
  count(Mid_Lane, name = "Wins", sort = TRUE)


Radiant_Mid_Lane_Total <- Dota_2_Stats_ALT %>%
  select(Radiant_Mid_Lane)
Radiant_Mid_Lane_Total


Renamed_Radiant_Mid_Lane_Total <- rename(Radiant_Mid_Lane_Total, Mid_Lane = "Radiant_Mid_Lane")


Dire_Mid_Lane_Total <- Dota_2_Stats_ALT %>%
  select(Dire_Mid_Lane)


Renamed_Dire_Mid_Lane_Total <- rename(Dire_Mid_Lane_Total, Mid_Lane = "Dire_Mid_Lane")


Mid_Lane_Total_Combined <- rbind(Renamed_Radiant_Mid_Lane_Total, Renamed_Dire_Mid_Lane_Total)


Mid_Lane_Total_Combined_Counted <- Mid_Lane_Total_Combined %>%
  count(Mid_Lane, name = "Total_Games", sort = TRUE)


Mid_Lane_Merged <- merge(x = Mid_Lane_Winners_Combined_Counted, y = Mid_Lane_Total_Combined_Counted, all.y = TRUE)

Mid_Lane_Win_Percentages <- Mid_Lane_Merged %>%
  mutate(Win_Percentage = Wins / Total_Games)

Mid_Lane_Win_Percentages_Arranged <- arrange(Mid_Lane_Win_Percentages,desc(Win_Percentage), desc(Total_Games))


Mid_Lane_Win_Percentages_Arranged


Mid_Lane_Win_Percentages_Ranked_2 <- Mid_Lane_Win_Percentages %>%
  mutate(Ranking_2 = Wins * Wins / Total_Games) %>%
  arrange(desc(Ranking_2))
Mid_Lane_Win_Percentages_Ranked_2
```


## Faceless Void Tinkering


```{r Faceless Void Stats, Echo = TRUE}
Faceless_Void_Games <- 
  
  Dota_2_Stats_ALT %>%
    filter_all(any_vars(. %in% c(Faceless_Void))) %>%
    count()


Faceless_Void_Wins <- 
  
  filter(Dota_2_Stats_ALT, Radiant_Safe_Lane == Faceless_Void & Radiant_Win_TF == TRUE | Dire_Safe_Lane == Faceless_Void & Radiant_Win_TF == FALSE) %>%
  count()

  
Faceless_Void_Win_Percentage <- Faceless_Void_Wins / Faceless_Void_Games


Faceless_Void_Win_Percentage

```