---
title: "Single_match_data"
format: html
editor: visual
---

## Packages Used

```{r}
library(tidyverse)
library(httr)
library(jsonlite)
library(mongolite)
```

## HEROES LIST (will use later)


## Hero_df <- fromJSON("D:/RFiles/dota2matches/heroesList.json")
## Hero_df


## My Query

```{r}
my_query <- 'query myMatchQuery {
  match(id: 8051303289) {
    id
    didRadiantWin
    durationSeconds
    analysisOutcome
    firstBloodTime
    players {
      matchId
      kills
      playerSlot
      steamAccountId
      isRadiant
      isVictory
      heroId
      gameVersionId
      kills
      deaths
      assists
      leaverStatus
      numLastHits
      numDenies
      goldPerMinute
      networth
      experiencePerMinute
      level
      gold
      goldSpent
      heroDamage
      towerDamage
      heroHealing
      partyId
      isRandom
      lane
      position
      streakPrediction
      intentionalFeeding
      role
      roleBasic
      imp
      award
      item0Id
      item1Id
      item2Id
      item3Id
      item4Id
      item5Id
      backpack0Id
      backpack1Id
      backpack2Id
      neutral0Id
      stats {
        matchId
        steamAccountId
        gameVersionId
        level
        networthPerMinute
        experiencePerMinute
        lastHitsPerMinute
        deniesPerMinute
        towerDamageReport {
          npcId
          damage
          damageCreeps
          damageFromAbility
        }
        goldPerMinute
        impPerMinute
        itemPurchases {
          time
          itemId
        }
        wards {
          time
          type
          positionX
          positionY
        }
        runes {
          time
          rune
        }
      }playbackData {
        killEvents {
        	time
					attacker
					isFromIllusion
          target
          byAbility
          byItem
          gold
          xp
          positionX
          positionY
          assist 
          isSolo
          isGank
          isInvisible
          isSmoke
          isTpRecently
          isRuneEffected
        }
        deathEvents {
          time
          attacker
          isFromIllusion
          target
          byAbility
          byItem
          goldFed
          xpFed
          timeDead
          reliableGold
          unreliableGold
          positionX
          positionY
          goldLost
          assist
          isWardWalkThrough
          isAttemptTpOut
          isDieBack
          isBurst
          isEngagedOnDeath
          hasHealAvailable
          isTracked
          isFeed
        }
        assistEvents {
          time
          attacker
          target
          gold
          xp
          subTime
          positionX
          positionY
        }
      }
    } 
    bottomLaneOutcome
    midLaneOutcome
    topLaneOutcome
    }
}'
```

## POST Call (fixed the empty "null" fields)

```{r}
stratz_url <- "https://api.stratz.com/graphql"

token <- "eyJhbGciOiJIUzI1NiIsInR5cCI6IkpXVCJ9.eyJTdWJqZWN0IjoiMzBmYmIyNzMtNzQ0MC00ZGUyLTg3OGYtODJiNjY3NDkwYzlkIiwiU3RlYW1JZCI6IjkyOTM2Njc5IiwibmJmIjoxNzMyNDU5MTY4LCJleHAiOjE3NjM5OTUxNjgsImlhdCI6MTczMjQ1OTE2OCwiaXNzIjoiaHR0cHM6Ly9hcGkuc3RyYXR6LmNvbSJ9.lxcjzNt63hHKon6w98fTQwYIs0osgyTIvWgVaV63UEo"


header <- paste("Bearer", 
                token, 
                sep = " ")

result <- POST(stratz_url, 
               body = list(query = my_query), 
               encode = "json", 
               add_headers('Content-Type'='application/json', 
                           Authorization = header,
                           'User-Agent' = "STRATZ_API"))
args(add_headers)

game1 <- content(result)

game1df <- do.call(rbind.data.frame, game1)

# unpacking the stats variables
  # unnest_wider(stats, names_sep = "_") %>%
  # select(-playbackData, -stats_itemPurchases, -stats_towerDamageReport, -stats_wards, -stats_runes)
game_data_df

# game1_json <-toJSON(
#   rapply(game1, 
#          function(z) 
#           if (length(z) == 1L) {
#             unbox(z) }
#           else z,
#             how = "replace"),
#   null = "null",
#   pretty = TRUE) 



mongoclient <- mongo(collection ="Matchdata", db = "Dota2", url = "mongodb://127.0.0.1:27017/?directConnection=true&serverSelectionTimeoutMS=2000&appName=Dota2MongoApp")
resultset <- mongoclient$insert(game1df)

## reference maybe resultset$data$match$players

# OLD CODE
# write(game1_json, "test3.json")
# 
# new_game_1 <- fromJSON("./test3.json")

```

##### Unnested dataframe

```{r}
game_data_df <- new_game_1$data$match$players %>%
  unnest_wider(stats, names_sep = "_") %>%
  select(-playbackData, -stats_itemPurchases, -stats_towerDamageReport, -stats_wards, -stats_runes)
game_data_df
```

##### Kill/Death/Assist (KDA) events

```{r}
game1killEvents <- new_game_1$data$match$players$playbackData$killEvents
game1sdeathEvents <- new_game_1$data$match$players$playbackData$deathEvents
game1assistEvents <- new_game_1$data$match$players$playbackData$assistEvents

Bot_lane_Result <- rep(new_game_1$data$match$bottomLaneOutcome, length = 10)
Top_lane_Result <- rep(new_game_1$data$match$topLaneOutcome, length = 10)
Mid_lane_Result <- rep(new_game_1$data$match$midLaneOutcome, length = 10)
```

##### Kills

```{r}
kills_10Minutes <- rep(0, length(game1killEvents))

for (i in 1:length(game1killEvents)) {
for (j in 1:length(game1killEvents[[i]]$time)) { 
    if (game1killEvents[[i]]$time[j] <= 600) {
      kills_10Minutes[i] <- kills_10Minutes[i] + 1
    }
  kills_10Minutes <- kills_10Minutes
}
}
kills_10Minutes
```

##### Deaths

```{r}
deaths_10Minutes <- rep(0, length(game1sdeathEvents))


for (i in 1:length(game1sdeathEvents)) {
for (j in 1:length(game1sdeathEvents[[i]]$time)) { 
    if (game1sdeathEvents[[i]]$time[j] <= 600) {
      deaths_10Minutes[i] <- deaths_10Minutes[i] + 1
    }
  deaths_10Minutes <- deaths_10Minutes
}
}
deaths_10Minutes
```

##### Assists

```{r}
assists_10Minutes <- rep(0, length(game1assistEvents))


for (i in 1:length(game1assistEvents)) {
for (j in 1:length(game1assistEvents[[i]]$time)) { 
    if (game1assistEvents[[i]]$time[j] <= 600) {
      assists_10Minutes[i] <- assists_10Minutes[i] + 1
    }
  assists_10Minutes <- assists_10Minutes
}
}
assists_10Minutes
```

##### Time taken to reach lvl 6

```{r}
lvl6_Time <- c()
for (i in 1:length(game_data_df$stats_level)) {
  lvl6_Time[i] <- game_data_df$stats_level[[i]][[1]][6]
}
lvl6_Time
```

###### Networth 10 min

```{r}
networth_10Min <- c()
for (i in 1:length(game_data_df$stats_networthPerMinute)) {
  networth_10Min[i] <- game_data_df$stats_networthPerMinute[[i]][[1]][11]
}
networth_10Min
```

##### Exp 10 Min

```{r}
exp_10Min <- c()
for (i in 1:length(game_data_df$stats_experiencePerMinute)) {
  exp_10Min[i] <- sum(game_data_df$stats_experiencePerMinute[[i]][[1]][1:10])
}
exp_10Min
```

##### Last Hits 10 Min

```{r}
last_hits_10Min <- c()
for (i in 1:length(game_data_df$stats_lastHitsPerMinute)) {
  last_hits_10Min[i] <- sum(game_data_df$stats_lastHitsPerMinute[[i]][[1]][1:10])
}
last_hits_10Min
```

##### Denies 10 Min

```{r}
denies_10Min <- c()
for (i in 1:length(game_data_df$stats_deniesPerMinute)) {
  denies_10Min[i] <- sum(game_data_df$stats_deniesPerMinute[[i]][[1]][1:10])
}
denies_10Min
```

## Wrangled Df

```{r}
game_data_df$kills_10_Minutes <- kills_10Minutes
game_data_df$deaths_10_Minutes <-deaths_10Minutes
game_data_df$assists_10_Minutes <-assists_10Minutes

game_data_df_10Min <- game_data_df %>%
  mutate(top_lane_outcome = Top_lane_Result,
         mid_lane_outcome = Mid_lane_Result,
         bot_lane_outcome = Bot_lane_Result,
         networth_10min = networth_10Min,
         exp_10min = exp_10Min,
         netexp_10min = networth_10Min + exp_10Min,
         last_hits_10min = last_hits_10Min,
         denies_10min = denies_10Min,
         time_lvl_6 = lvl6_Time,
         .after = matchId) %>%
  relocate(heroId, 
           isRadiant,
           position,
           top_lane_outcome,
           mid_lane_outcome,
           bot_lane_outcome,
           netexp_10min,
           kills_10_Minutes,
           deaths_10_Minutes,
           assists_10_Minutes,
           
           .after = matchId)


# THIS IS MY LATEST RESULT DATAFRAME
game_data_df_10Min %>%
  select(-intentionalFeeding, -stats_matchId, -stats_gameVersionId, -stats_steamAccountId, -stats_level, -stats_networthPerMinute, -stats_experiencePerMinute, -stats_lastHitsPerMinute, -stats_deniesPerMinute, -stats_goldPerMinute, -stats_impPerMinute)
```

## Attempting to replace heroId with the hero names for my own sanity.

```{r}
game_data_df_10Min[["heroId"]] <- Hero_df[ match(game_data_df_10Min[['heroId']], Hero_df[['id']] ) , 'localized_name']
game_data_df_10Min
```

```{r}
game_data_df_10Min %>%
  filter(isRadiant == TRUE, position == "POSITION_1" | position == "POSITION_5")
```




